Image Caption Generation With CLIP+GPT-2 Model

### 2025-05-04 Latex_Paper/Paper.tex
update all

\subsection{Future Work}
\begin{itemize}
  \item Extend to other self-supervised methods (e.g., BYOL, MoCo).
  \item Apply to domain adaptation tasks.
  \item Explore contrastive learning for text or multimodal applications.
\end{itemize}

\section{Conclusion}
Our empirical study demonstrates the effectiveness of contrastive learning via SimCLR for representation
learning. By systematically evaluating augmentation pipelines, batch sizes, and loss functions, we provide
insights into optimizing contrastive learning for different datasets.
\pagebreak
\begin{thebibliography}{99}
    \bibitem{Nukrai2022}
    Nukrai, D., Mokady, R., \& Globerson, A. (2022). Text-Only Training for Image Captioning using Noise-Injected CLIP. https://doi.org/10.48448/n7sq-p557

>>>>

\subsection{Future Work}
\begin{itemize}
  \item 
  \item 
  \item 
\end{itemize}

\section{Conclusion}

\pagebreak
\begin{thebibliography}{99}
    \bibitem{Nukrai2022}
    Nukrai, D., Mokady, R., \& Globerson, A. (2022). Text-Only Training for Image Captioning using Noise-Injected CLIP. https://doi.org/10.48448/n7sq-p557
